---
title: "573project"
author: "Meltem Ozcan"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r read-functions, message=FALSE, warning=FALSE}
library(blavaan) # to fit Bayesian latent variable models
library(dplyr)
library(bayesplot)
library(posterior)
library(here)
source('573_helper.R') #read in helper functions
```

```{r data-prep}
data <- read.table("IPIPFFM.dat", header = TRUE)
head(data)
agree_m <- data[data$sex == 1, c("a2", "a5", "a7", "a9")] #239 males
agree_f <- data[data$sex == 2, c("a2", "a5", "a7", "a9") ] #325 females
agree <- data[, c("sex", "a2", "a5", "a7", "a9")]
consc <- data[, c("sex", "c3", "c4", "c8", "c9")]
extr <- data[, c("sex", "e1", "e4", "e6", "e7")]
neur <- data[, c("sex", "n1", "n2", "n6", "n8")]
open <- data[, c("sex", "i2", "i8", "i9", "i10")]  
```

## Fit Bayesian CFA and compute posteriors

```{r cfa-models}
m_a <- 'A =~  a2 + a5  + a7 + a9
          a2 ~~ a5'
m_c <- 'C =~  c3 + c4 + c8 + c9'
m_e <- 'E =~ e1 + e4 + e6 + e7
          e4 ~~ e7  '
m_n <- 'N =~ n1 + n2 + n6 + n8'
m_o <- 'O =~ i2 + i8 + i9 + i10
          i2 ~~ i10
          i8 ~~ i9'
```

### Fit Bayesian CFA and compute posteriors: Agreeableness 

```{r bcfa_agree}
set.seed(7)

agree_fit <- bcfa(m_a, data = agree, group = "sex",
               group.equal = c("loadings", "Intercepts", "residuals"),
               group.partial = c("a2 ~ 1"), 
               std.lv = TRUE, save.lvs = TRUE, n.chains = 3)
summary(agree_fit)
blavInspect(agree_fit, "est")

#Get the posterior distribution of the latent variable conditioned on the
#observed variables
agree_fit.lvs <- blavInspect(agree_fit, "lvs") #list of 3, each is 1000 x 564
agree_post_eta <- rbind(agree_fit.lvs[[1]], agree_fit.lvs[[2]],
                           agree_fit.lvs[[3]]) #combine the chains
#The posterior expected value of observed variables conditioned on the sampled latent variables
agree_fit.ypred <- blavPredict(agree_fit, type = "ypred")
#dim(agree_fit.ypred[[1]]) # agree_fit.ypred = list of 3000, each 564 x 4.

agree_post_z <- matrix(ncol = 3000, nrow = 564)
rowSums <- vector(mode = "list", length = 3000)
for(i in seq_along(1:length(agree_fit.ypred))){
  agree_post_z[,i] <- t(rowSums(agree_fit.ypred[[i]]))
}

agree_post_CAI <- get_posterior_CAI(agree_post_eta, 
                                    t(agree_post_z), 0.15, agree$sex,
                                    ref = "2", foc = "1")
```

### Fit Bayesian CFA and compute posteriors: Conscientiousness 
```{r bcfa_consc}
set.seed(7)

consc_fit <- bcfa(m_c, data = consc, group = "sex",
               group.equal = c("loadings", "Intercepts", "residuals"),
               group.partial = c("c3 ~ 1"), 
               std.lv = TRUE, save.lvs = TRUE, n.chains = 3)
summary(consc_fit)
blavInspect(consc_fit, "est")

#Get the posterior distribution of the latent variable conditioned on the
#observed variables
consc_fit.lvs <- blavInspect(consc_fit, "lvs") #list of 3, each is 1000 x 564
consc_post_eta <- rbind(consc_fit.lvs[[1]], consc_fit.lvs[[2]],
                           consc_fit.lvs[[3]]) #combine the chains
#The posterior expected value of observed variables conditioned on the sampled latent variables
consc_fit.ypred <- blavPredict(consc_fit, type = "ypred")
consc_post_z <- matrix(ncol = 3000, nrow = 564)
rowSums <- vector(mode = "list", length = 3000)
for(i in seq_along(1:length(consc_fit.ypred))){
  consc_post_z[,i] <- t(rowSums(consc_fit.ypred[[i]]))
}

consc_post_CAI <- get_posterior_CAI(consc_post_eta, 
                                    t(consc_post_z), 0.15, consc$sex,
                                    ref = "2", foc = "1")
```

### Fit Bayesian CFA and compute posteriors: Extraversion 

```{r bcfa_extr}
set.seed(7)

extr_fit <- bcfa(m_e, data = extr, group = "sex",
               group.equal = c("loadings", "Intercepts", "residuals"),
               group.partial = c("e1 ~ 1"), 
               std.lv = TRUE, save.lvs = TRUE, n.chains = 3)
summary(extr_fit)
blavInspect(extr_fit, "est")

#Get the posterior distribution of the latent variable conditioned on the
#observed variables
extr_fit.lvs <- blavInspect(extr_fit, "lvs") #list of 3, each is 1000 x 564
extr_post_eta <- rbind(extr_fit.lvs[[1]], extr_fit.lvs[[2]],
                           extr_fit.lvs[[3]]) #combine the chains
#The posterior expected value of observed variables conditioned on the sampled latent variables
extr_fit.ypred <- blavPredict(extr_fit, type = "ypred")

extr_post_z <- matrix(ncol = 3000, nrow = 564)
rowSums <- vector(mode = "list", length = 3000)
for(i in seq_along(1:length(extr_fit.ypred))){
  extr_post_z[,i] <- t(rowSums(extr_fit.ypred[[i]]))
}

extr_post_CAI <- get_posterior_CAI(extr_post_eta, 
                                    t(extr_post_z), 0.15, extr$sex,
                                    ref = "2", foc = "1")
```

### Fit Bayesian CFA and compute posteriors: Neuroticism 

```{r bcfa_neur}
set.seed(7)

neur_fit <- bcfa(m_n, data = neur, group = "sex",
               group.equal = c("loadings", "Intercepts", "residuals"),
               group.partial = c("n1 ~ 1"), 
               std.lv = TRUE, save.lvs=TRUE, n.chains = 3)
summary(neur_fit)
blavInspect(neur_fit, "est")

#Get the posterior distribution of the latent variable conditioned on the
#observed variables
neur_fit.lvs <- blavInspect(neur_fit, "lvs") #list of 3, each is 1000 x 564
neur_post_eta <- rbind(neur_fit.lvs[[1]], neur_fit.lvs[[2]],
                           neur_fit.lvs[[3]]) #combine the chains
#The posterior expected value of observed variables conditioned on the sampled latent variables
neur_fit.ypred <- blavPredict(neur_fit, type = "ypred")
neur_post_z <- matrix(ncol = 3000, nrow = 564)
rowSums <- vector(mode="list", length = 3000)
for(i in seq_along(1:length(neur_fit.ypred))){
  neur_post_z[,i] <- t(rowSums(neur_fit.ypred[[i]]))
}

neur_post_CAI <- get_posterior_CAI(neur_post_eta, 
                                    t(neur_post_z), 0.15, neur$sex,
                                    ref="2", foc="1")
```

### Fit Bayesian CFA and compute posteriors: Openness to Experience 

```{r bcfa_open}
set.seed(7)

open_fit <- bcfa(m_o, data = open, group = "sex",
               group.equal = c("loadings", "Intercepts", "residuals"),
               group.partial = c("i2 ~ 1"), 
               std.lv = TRUE, save.lvs=TRUE, n.chains = 3)
summary(open_fit)
blavInspect(open_fit, "est")

#Get the posterior distribution of the latent variable conditioned on the
#observed variables
open_fit.lvs <- blavInspect(open_fit, "lvs") #list of 3, each is 1000 x 564
open_post_eta <- rbind(open_fit.lvs[[1]], open_fit.lvs[[2]],
                           open_fit.lvs[[3]]) #combine the chains
#The posterior expected value of observed variables conditioned on the sampled latent variables
open_fit.ypred <- blavPredict(open_fit, type = "ypred")
open_post_z <- matrix(ncol = 3000, nrow = 564)
rowSums <- vector(mode = "list", length = 3000)
for(i in seq_along(1:length(open_fit.ypred))){
  open_post_z[,i] <- t(rowSums(open_fit.ypred[[i]]))
}

open_post_CAI <- get_posterior_CAI(open_post_eta, 
                                    t(open_post_z), 0.15, open$sex,
                                    ref = "2", foc = "1")
```


## Convergence checks of MCMC

### Convergence checks of MCMC: Agreeableness
```{r agree_convergence_prep}
# Check for convergence, mixing
a_mcmc <- blavInspect(agree_fit, "mcmc") # mcmc draws for each parameter
a_mcmc3 <- rbind(a_mcmc[[1]], a_mcmc[[2]], a_mcmc[[3]]) # combine chains
a_draws <- a_mcmc3[,c(1:13,18,23,24,28)] # remove duplicates from combined chain
a_mcmc[[1]] <- a_mcmc[[1]][,c(1:13,18,23,24,28)] # remove duplicates in each chain
a_mcmc[[2]] <- a_mcmc[[2]][,c(1:13,18,23,24,28)]
a_mcmc[[3]] <- a_mcmc[[3]][,c(1:13,18,23,24,28)]

colnames(a_draws) <- colnames(a_mcmc[[1]]) <- colnames(a_mcmc[[2]]) <-
  colnames(a_mcmc[[3]]) <- c("lambda1", "lambda2", "lambda3", "lambda4", 
                             "Theta_cov_r", "Theta_var1", "Theta_var2", 
                             "Theta_var3", "Theta_var4", "nu1_r", "nu2", "nu3", 
                             "nu4", "Theta_cov_f", "Psi_r", "nu1_f", "alpha_f" )
```

```{r agree-convergence}
mcmc_trace(a_mcmc, regex_pars=c("lambda", "Psi", "alpha")) 
mcmc_trace(a_mcmc, regex_pars="Theta") 
mcmc_trace(a_mcmc, regex_pars="nu")
mcmc_rank_hist(a_mcmc,regex_pars=c("lambda", "Psi", "alpha"))
mcmc_rank_hist(a_mcmc,regex_pars=c("Theta"))
mcmc_rank_hist(a_mcmc,regex_pars=c("nu"))
```


### Convergence checks of MCMC: Conscientiousness


```{r consc_convergence_prep}
# Check for convergence, mixing
c_mcmc <- blavInspect(consc_fit, "mcmc") # mcmc draws for each parameter
c_mcmc3 <- rbind(c_mcmc[[1]], c_mcmc[[2]], c_mcmc[[3]]) # combine chains
c_draws <- c_mcmc3[,c(1:12, 21, 26)] # remove duplicates from combined chain
c_mcmc[[1]] <- c_mcmc[[1]][,c(1:12, 21, 26)] # remove duplicates in each chain
c_mcmc[[2]] <- c_mcmc[[2]][,c(1:12, 21, 26)]
c_mcmc[[3]] <- c_mcmc[[3]][,c(1:12, 21, 26)]

colnames(c_draws) <- colnames(c_mcmc[[1]]) <- colnames(c_mcmc[[2]]) <-
  colnames(c_mcmc[[3]]) <- c("lambda1", "lambda2", "lambda3", "lambda4", 
                            "Theta_var1", "Theta_var2", "Theta_var3", "Theta_var4",
                            "nu1", "nu2", "nu3", "nu4", 
                            "Psi_f", "alpha_f" )
```

```{r c-convergence}
mcmc_trace(c_mcmc, regex_pars=c("lambda", "Psi", "alpha")) 
mcmc_trace(c_mcmc, regex_pars="Theta") 
mcmc_trace(c_mcmc, regex_pars="nu")
mcmc_rank_hist(c_mcmc,regex_pars=c("lambda", "Psi", "alpha"))
mcmc_rank_hist(c_mcmc,regex_pars=c("Theta"))
mcmc_rank_hist(c_mcmc,regex_pars=c("nu"))
```


### Convergence checks of MCMC: Extraversion

```{r extr_convergence_prep}
# Check for convergence, mixing
e_mcmc <- blavInspect(extr_fit, "mcmc") # mcmc draws for each parameter
e_mcmc3 <- rbind(e_mcmc[[1]], e_mcmc[[2]], e_mcmc[[3]]) # combine chains
e_draws <- e_mcmc3[,c(1:13,18,23,24,28)] # remove duplicates from combined chain
e_mcmc[[1]] <- e_mcmc[[1]][,c(1:13,18,23,24,28)] # remove duplicates in each chain
e_mcmc[[2]] <- e_mcmc[[2]][,c(1:13,18,23,24,28)]
e_mcmc[[3]] <- e_mcmc[[3]][,c(1:13,18,23,24,28)]

colnames(e_draws) <- colnames(e_mcmc[[1]]) <- colnames(e_mcmc[[2]]) <-
  colnames(e_mcmc[[3]]) <- c("lambda1", "lambda2", "lambda3", "lambda4", 
                             "Theta_cov_r", "Theta_var1", "Theta_var2", 
                             "Theta_var3", "Theta_var4", "nu1_r", "nu2", "nu3", 
                             "nu4", "Theta_cov_f", "Psi_r", "nu1_f", "alpha_f" )
```

```{r e-convergence}
mcmc_trace(e_mcmc, regex_pars=c("lambda", "Psi", "alpha")) 
mcmc_trace(e_mcmc, regex_pars="Theta") 
mcmc_trace(e_mcmc, regex_pars="nu")
mcmc_rank_hist(e_mcmc,regex_pars=c("lambda", "Psi", "alpha"))
mcmc_rank_hist(e_mcmc,regex_pars=c("Theta"))
mcmc_rank_hist(e_mcmc,regex_pars=c("nu"))
```

### Convergence checks of MCMC: Neuroticsm


```{r n_convergence_prep}
# Check for convergence, mixing
n_mcmc <- blavInspect(neur_fit, "mcmc") # mcmc draws for each parameter
n_mcmc3 <- rbind(n_mcmc[[1]], n_mcmc[[2]], n_mcmc[[3]]) # combine chains
n_draws <- n_mcmc3[,c(1:12, 21, 26)] # remove duplicates from combined chain
n_mcmc[[1]] <- n_mcmc[[1]][,c(1:12, 21, 26)] # remove duplicates in each chain
n_mcmc[[2]] <- n_mcmc[[2]][,c(1:12, 21, 26)]
n_mcmc[[3]] <- n_mcmc[[3]][,c(1:12, 21, 26)]

colnames(n_draws) <- colnames(n_mcmc[[1]]) <- colnames(n_mcmc[[2]]) <-
  colnames(n_mcmc[[3]]) <- c("lambda1", "lambda2", "lambda3", "lambda4", 
                            "Theta_var1", "Theta_var2", "Theta_var3", "Theta_var4",
                            "nu1", "nu2", "nu3", "nu4", 
                            "Psi_f", "alpha_f" )
```

```{r n-convergence}
mcmc_trace(n_mcmc, regex_pars=c("lambda", "Psi", "alpha")) 
mcmc_trace(n_mcmc, regex_pars="Theta") 
mcmc_trace(n_mcmc, regex_pars="nu")
mcmc_rank_hist(n_mcmc,regex_pars=c("lambda", "Psi", "alpha"))
mcmc_rank_hist(n_mcmc,regex_pars=c("Theta"))
mcmc_rank_hist(n_mcmc,regex_pars=c("nu"))
```



### Convergence checks of MCMC: Openness to Experience

```{r open_convergence_prep}
# Check for convergence, mixing
o_mcmc <- blavInspect(open_fit, "mcmc") # mcmc draws for each parameter
o_mcmc3 <- rbind(o_mcmc[[1]], o_mcmc[[2]], o_mcmc[[3]]) # combine chains
o_draws <- o_mcmc3[,c(1:14, 19, 20,  25, 26, 30)] # remove duplicates from combined chain
o_mcmc[[1]] <- o_mcmc[[1]][,c(1:14, 19, 20,  25, 26, 30)] # remove duplicates in each chain
o_mcmc[[2]] <- o_mcmc[[2]][,c(1:14, 19, 20, 25, 26, 30)]
o_mcmc[[3]] <- o_mcmc[[3]][,c(1:14, 19, 20,  25, 26, 30)]

colnames(o_draws) <- colnames(o_mcmc[[1]]) <- colnames(o_mcmc[[2]]) <-
  colnames(o_mcmc[[3]]) <- c("lambda1", "lambda2", "lambda3", "lambda4", 
                             "Theta_cov_r1", "Theta_cov_r2",
                             "Theta_var1", "Theta_var2","Theta_var3", "Theta_var4",
                             "nu1_r", "nu2", "nu3", "nu4", 
                             "Theta_cov_f1","Theta_cov_f2", 
                             "Psi_r", "nu1_f", "alpha_f" )
```

```{r o-convergence}
mcmc_trace(o_mcmc, regex_pars=c("lambda", "Psi", "alpha")) 
mcmc_trace(o_mcmc, regex_pars="Theta") 
mcmc_trace(o_mcmc, regex_pars="nu")
mcmc_rank_hist(o_mcmc,regex_pars=c("lambda", "Psi", "alpha"))
mcmc_rank_hist(o_mcmc,regex_pars=c("Theta"))
mcmc_rank_hist(o_mcmc,regex_pars=c("nu"))
```
```{r priors}
# default priors, same for all
blavInspect(agree_fit, "dp")
blavInspect(consc_fit, "dp")
blavInspect(extr_fit, "dp")
blavInspect(neur_fit, "dp")
blavInspect(open_fit, "dp")
```


## Posterior summaries of MCMC draws for model parameters

### Posterior summaries: Agreeableness model parameters

```{r a_summary}
a_mcmc %>% summarize_draws() %>% knitr::kable(digits = 2)
```


### Posterior summaries: Conscientiousness model parameters

```{r c_summary}
c_mcmc %>% summarize_draws() %>% knitr::kable(digits = 2)
```

### Posterior summaries: Extraversion model parameters

```{r e_summary}
e_mcmc %>% summarize_draws() %>% knitr::kable(digits = 2)
```


### Posterior summaries: Neuroticism model parameters

```{r n_summary}
n_mcmc %>% summarize_draws() %>% knitr::kable(digits = 2)
```


### Posterior summaries: Openness to Experience model parameters

```{r o_summary}
o_mcmc %>% summarize_draws() %>% knitr::kable(digits = 2)
```



```{r overall_CAI_summaries}

a_cai_summary <- summarize_draws(agree_post_CAI$overall)
a_cai_summary[,2:8] <- round(a_cai_summary[,2:8],2)
a_cai_summary[,9:10] <- round(a_cai_summary[,9:10])
a_cai_summary%>% knitr::kable()
c_cai_summary <- summarize_draws(consc_post_CAI$overall)
c_cai_summary[,2:8] <- round(c_cai_summary[,2:8],2)
c_cai_summary[,9:10] <- round(c_cai_summary[,9:10])
c_cai_summary%>% knitr::kable()
e_cai_summary <- summarize_draws(extr_post_CAI$overall)
e_cai_summary[,2:8] <- round(e_cai_summary[,2:8],2)
e_cai_summary[,9:10] <- round(e_cai_summary[,9:10])
e_cai_summary%>% knitr::kable()
n_cai_summary <- summarize_draws(neur_post_CAI$overall)
n_cai_summary[,2:8] <- round(n_cai_summary[,2:8],2)
n_cai_summary[,9:10] <- round(n_cai_summary[,9:10])
n_cai_summary%>% knitr::kable()
o_cai_summary <- summarize_draws(open_post_CAI$overall)
o_cai_summary[,2:8] <- round(o_cai_summary[,2:8],2)
o_cai_summary[,9:10] <- round(o_cai_summary[,9:10])
o_cai_summary%>% knitr::kable()
```

```{r ref_CAI_summaries}
a_cai_summaryr <- summarize_draws(agree_post_CAI$reference)
a_cai_summaryr[,2:8] <- round(a_cai_summaryr[,2:8],2)
a_cai_summaryr[,9:10] <- round(a_cai_summaryr[,9:10])
a_cai_summaryr%>% knitr::kable()
c_cai_summaryr <- summarize_draws(consc_post_CAI$reference)
c_cai_summaryr[,2:8] <- round(c_cai_summaryr[,2:8],2)
c_cai_summaryr[,9:10] <- round(c_cai_summaryr[,9:10])
c_cai_summaryr%>% knitr::kable()
e_cai_summaryr <- summarize_draws(extr_post_CAI$reference)
e_cai_summaryr[,2:8] <- round(e_cai_summaryr[,2:8],2)
e_cai_summaryr[,9:10] <- round(e_cai_summaryr[,9:10])
e_cai_summaryr%>% knitr::kable()
n_cai_summaryr <- summarize_draws(neur_post_CAI$reference)
n_cai_summaryr[,2:8] <- round(n_cai_summaryr[,2:8],2)
n_cai_summaryr[,9:10] <- round(n_cai_summaryr[,9:10])
n_cai_summaryr%>% knitr::kable()
o_cai_summaryr <- summarize_draws(open_post_CAI$reference)
o_cai_summaryr[,2:8] <- round(o_cai_summaryr[,2:8],2)
o_cai_summaryr[,9:10] <- round(o_cai_summaryr[,9:10])
o_cai_summaryr%>% knitr::kable()
```


```{r f_CAI_summaries}

a_cai_summaryf <- summarize_draws(agree_post_CAI$focal)
a_cai_summaryf[,2:8] <- round(a_cai_summaryf[,2:8],2)
a_cai_summaryf[,9:10] <- round(a_cai_summaryf[,9:10])
a_cai_summaryf%>% knitr::kable()
c_cai_summaryf <- summarize_draws(consc_post_CAI$focal)
c_cai_summaryf[,2:8] <- round(c_cai_summaryf[,2:8],2)
c_cai_summaryf[,9:10] <- round(c_cai_summaryf[,9:10])
c_cai_summaryf%>% knitr::kable()
e_cai_summaryf <- summarize_draws(extr_post_CAI$focal)
e_cai_summaryf[,2:8] <- round(e_cai_summaryf[,2:8],2)
e_cai_summaryf[,9:10] <- round(e_cai_summaryf[,9:10])
e_cai_summaryf%>% knitr::kable()
n_cai_summaryf <- summarize_draws(neur_post_CAI$focal)
n_cai_summaryf[,2:8] <- round(n_cai_summaryf[,2:8],2)
n_cai_summaryf[,9:10] <- round(n_cai_summaryf[,9:10])
n_cai_summaryf%>% knitr::kable()
o_cai_summaryf <- summarize_draws(open_post_CAI$focal)
o_cai_summaryf[,2:8] <- round(o_cai_summaryf[,2:8],2)
o_cai_summaryf[,9:10] <- round(o_cai_summaryf[,9:10])
o_cai_summaryf%>% knitr::kable()
```


## Posterior distributions of classification accuracy indices

### Agreeableness, group: F

```{r}
mcmc_areas(agree_post_CAI$reference, pars = c( "SR", "SE", "SP"))
```

### Agreeableness, group: M

```{r}
mcmc_areas(agree_post_CAI$focal, pars = c( "SR", "SE", "SP"))
```

### Conscientiousness, group: F

```{r}
mcmc_areas(consc_post_CAI$reference, pars = c( "SR", "SE", "SP"))
```

### Conscientiousness, group: M

```{r}
mcmc_areas(consc_post_CAI$focal, pars = c( "SR", "SE", "SP"))
```

### Extraversion, group: F

```{r}
mcmc_areas(extr_post_CAI$reference, pars = c( "SR", "SE", "SP"))
```

### Extraversion, group: M

```{r}
mcmc_areas(extr_post_CAI$focal, pars = c( "SR", "SE", "SP"))
```

### Neuroticism, group: F

```{r}
mcmc_areas(neur_post_CAI$reference, pars = c( "SR", "SE", "SP"))
```

### Neuroticism, group: M

```{r}
mcmc_areas(neur_post_CAI$focal, pars = c( "SR", "SE", "SP"))
```

### Openness to Experience, group: F

```{r}
mcmc_areas(open_post_CAI$reference, pars = c( "SR", "SE", "SP"))
```

### Openness to Experience, group: M

```{r}
mcmc_areas(open_post_CAI$focal, pars = c( "SR", "SE", "SP"))
```




## Posterior distribution of Cohen's h computed for the difference in classification accuracy indices

\begin{align}
    \text{h} = 2\text{arcsin}\left(\sqrt{\text{CAI}_1}\right)-2\text{arcsin}\left(\sqrt{\text{CAI}_2}\right)
\end{align}

```{r h-summaries}
# Agreeableness
agree_h <- summarize_draws(agree_post_CAI$h)
agree_h[,2:8] <- round(agree_h[,2:8],2)
agree_h[,9:10] <- round(agree_h[,9:10])
agree_h %>% knitr::kable()
# Conscientiousness
consc_h <- summarize_draws(consc_post_CAI$h)
consc_h[,2:8] <- round(consc_h[,2:8],2)
consc_h[,9:10] <- round(consc_h[,9:10])
consc_h %>% knitr::kable()
# Extraversion
extra_h <- summarize_draws(extr_post_CAI$h)
extra_h[,2:8] <- round(extra_h[,2:8],2)
extra_h[,9:10] <- round(extra_h[,9:10])
extra_h %>% knitr::kable()
# Neuroticism
neur_h <- summarize_draws(neur_post_CAI$h)
neur_h[,2:8] <- round(neur_h[,2:8],2)
neur_h[,9:10] <- round(neur_h[,9:10])
neur_h %>% knitr::kable()
# Openness to Experience
open_h <- summarize_draws(open_post_CAI$h)
open_h[,2:8] <- round(open_h[,2:8],2)
open_h[,9:10] <- round(open_h[,9:10])
open_h %>% knitr::kable()
```



### Posterior distribution of Cohen's h

```{r h areas}
par(mfrow=c(2,3))
# Agreeableness
mcmc_areas(agree_post_CAI$h)
# Conscientiousness
mcmc_areas(consc_post_CAI$h)
# Extraversion
mcmc_areas(extr_post_CAI$h)
# Neuroticism
mcmc_areas(neur_post_CAI$h)
# Openness to Experience
mcmc_areas(open_post_CAI$h)
```






